Preliminary Thesis Defence

### 2013-11-13 draft.Rnw
commit before merge
running again
remove abstracts from articles
update to scrbook

\documentclass[a4paper]{report}
\usepackage{subfiles}
\usepackage{hyperref}

\title{Preliminary Thesis Defence}
%\subtitle{
%\begin{tabular}{rl}
%Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; Director, Centre for Finance and Development; jean-louis.arcand@graduateinstitute.ch}\\
%Second Reader:&Love Vanderwalle\footnote{Assistant Professor of Economics, The Graduate Institute, Geneva; lore.vandewalle@graduateinstitute.ch}
%\end{tabular}
%}

@@

\maketitle

@@

\chapter*{Introduction}
jade

\chapter{South Africa}
a la duflo

@@

\chapter*{End notes}

>>>>

\documentclass[a4paper]{scrbook}
\usepackage{subfiles}
\usepackage{hyperref}

\title{Preliminary Thesis Defence}
\subtitle{
\begin{tabular}{rl}
Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; Director, Centre for Finance and Development; jean-louis.arcand@graduateinstitute.ch}\\
Second Reader:&Love Vanderwalle\footnote{Assistant Professor of Economics, The Graduate Institute, Geneva; lore.vandewalle@graduateinstitute.ch}
\end{tabular}
}

@@

\frontmatter
\maketitle

@@

\chapter{Introduction}
jade

\mainmatter
\chapter{South Africa}
a la duflo

@@

\backmatter
\chapter{End notes}

### 2013-11-13 draft.tex
commit before merge
running again
remove abstracts from articles
removed \abstract from chapters
update to scrbook

\documentclass[a4paper]{report}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

@@

\title{Preliminary Thesis Defence}
%\subtitle{
%\begin{tabular}{rl}
%Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; Director, Centre for Finance and Development; jean-louis.arcand@graduateinstitute.ch}\\
%Second Reader:&Love Vanderwalle\footnote{Assistant Professor of Economics, The Graduate Institute, Geneva; lore.vandewalle@graduateinstitute.ch}
%\end{tabular}
%}

>>>>

\documentclass[a4paper]{scrbook}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

@@

\title{Preliminary Thesis Defence}
\subtitle{
\begin{tabular}{rl}
Supervisor:&Jean-Louis Arcand\footnote{Professor of Economics, The Graduate Institute, Geneva; Director, Centre for Finance and Development; jean-louis.arcand@graduateinstitute.ch}\\
Second Reader:&Love Vanderwalle\footnote{Assistant Professor of Economics, The Graduate Institute, Geneva; lore.vandewalle@graduateinstitute.ch}
\end{tabular}
}
